# Retrospective analysis summary for  my.syndromic

```{r}
#loading and preparing the data to work with
load("my.syndromic.RData")
require(vetsyn)
matrix.days <- x@observed
matrix.week.full <- convert_days_to_week(x@observed,x@dates)
matrix.week <- matrix.week.full[,-(1:2),drop=FALSE]
frequency=365
```

## Cattle
```{r}
#create time series
s=1
days    <-  matrix.days[,s]
days.ts <-  ts(days, start = c(x@dates$year[1], x@dates$yday[1]),
               frequency = frequency)
t = 1:length(days)

week    <-  matrix.week[,s]
week.ts <-  ts(week, start = c(matrix.week.full[1,2],as.numeric(substr(as.character(matrix.week.full[1,1]),7,8))),
               frequency = 52)
t.week <- 1:length(week)
```

```{r fig.width=10, fig.height=5}
#Plot series
plot(days.ts , xlab="Days", main="Daily")
plot(week.ts , xlab="Weeks",main="Weeks")
```

### Summary statistics
```{r}
#Percentiles
quantile(days,probs=c(0,0.25,0.5,0.75,1),names=FALSE)
round(mean(days),4)

#Number of days at minimum value
(countInMin <- length(which(days == min(days))))
(percentInMin <- round(((countInMin)/(length(days)))*100,2))
```

```{r fig.width=10, fig.height=5}
#ACF and PACF
acf(days,main="ACF for daily data")
pacf(days,main="PACF for daily data")
```

### Crude (visual) assessment of temporal effects
```{r fig.width=10, fig.height=5}
boxplot(days ~ x@dates$dow, main="Day of the Week")
boxplot(days ~ x@dates$month, main = "Month")
boxplot(days ~ x@dates$year, main = "Year")
```

### POISSON  Regression with DOW, month or sin/cos wave
```{r}
distribution="poisson"

month.f = as.factor (x@dates$month)
dow.f <- as.factor (x@dates$dow)
cos = cos (2*pi*t/frequency)
sin = sin (2*pi*t/frequency)
tminus1<-c(days[1],days[1:(length(days)-1)])
tminus2<-c(days[1:2],days[1:(length(days)-2)])
tminus3<-c(days[1:3],days[1:(length(days)-3)])
tminus4<-c(days[1:4],days[1:(length(days)-4)])
tminus5<-c(days[1:5],days[1:(length(days)-5)])
tminus6<-c(days[1:6],days[1:(length(days)-6)])
tminus7<-c(days[1:7],days[1:(length(days)-7)])

fit1 = glm(days~ dow.f, family=distribution)
fit1AR1 = glm(days~ dow.f + tminus1, family=distribution)
fit1AR2 = glm(days~ dow.f + tminus1+ tminus2, family=distribution)
fit1AR3 = glm(days~ dow.f + tminus1+ tminus2 + tminus3, family=distribution)
fit1AR4 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit1AR5 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit1AR6 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit1AR7 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)

fit2 = glm(days~ dow.f+ month.f, family=distribution)
fit2AR1 = glm(days~ dow.f+ month.f + tminus1, family=distribution)
fit2AR2 = glm(days~ dow.f+ month.f + tminus1+ tminus2, family=distribution)
fit2AR3 = glm(days~ dow.f+ month.f + tminus1+ tminus2 + tminus3, family=distribution)
fit2AR4 = glm(days~ dow.f+ month.f +
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit2AR5 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit2AR6 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit2AR7 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)

fit3 = glm(days~ dow.f+ cos + sin, family=distribution)
fit3AR1 = glm(days~ dow.f+ cos + sin + tminus1, family=distribution)
fit3AR2 = glm(days~ dow.f+ cos + sin + tminus1+ tminus2, family=distribution)
fit3AR3 = glm(days~ dow.f+ cos + sin + tminus1+ tminus2 + tminus3, family=distribution)
fit3AR4 = glm(days~ dow.f  + cos + sin + 
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit3AR5 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit3AR6 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit3AR7 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)
```


```{r}
#Printing AICs
AR1 <- c(fit1=fit1$aic,fit1AR1=fit1AR1$aic,fit1AR2=fit1AR2$aic,fit1AR3=fit1AR3$aic,
                          fit1AR4=fit1AR4$aic,fit1AR5=fit1AR5$aic,fit1AR6=fit1AR6$aic,fit1AR7=fit1AR7$aic)
AR2 <- c(fit2=fit2$aic,fit2AR1=fit2AR1$aic,fit2AR2=fit2AR2$aic,fit2AR3=fit2AR3$aic,
                          fit2AR4=fit2AR4$aic,fit2AR5=fit2AR5$aic,fit2AR6=fit2AR6$aic,fit2AR7=fit2AR7$aic)
AR3 <- c(fit3=fit3$aic,fit3AR1=fit3AR1$aic,fit3AR2=fit3AR2$aic,fit3AR3=fit3AR3$aic,
                          fit3AR4=fit3AR4$aic,fit3AR5=fit3AR5$aic,fit3AR6=fit3AR6$aic,fit3AR7=fit3AR7$aic)


print(AR1)
print(AR2)
print(AR3)

```

```{r fig.width=10, fig.height=5}
plot(t,days, type="l",main="Poisson regression")
lines(fit1$fit, col="red"   , lwd=2)
lines(fit2$fit, col="blue"  , lwd=2)
lines(fit3$fit, col="green" , lwd=2)
legend("topleft",pch=3,col=c("red","blue","green"),
                  c("Day-of-Week", "Day-of-Week+Month","Day-of-Week+sin/cos"))

### Negative Binomial Regression with DOW, month or sin/cos wave
```{r}
require(MASS)
fitNB1 = glm.nb(days~ dow.f)
fitNB1AR1 = glm.nb(days~ dow.f + tminus1)
fitNB1AR2 = glm.nb(days~ dow.f + tminus1+ tminus2)
fitNB1AR3 = glm.nb(days~ dow.f + tminus1+ tminus2 + tminus3)
fitNB1AR4 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB1AR5 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB1AR6 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB1AR7 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)

fitNB2 = glm.nb(days~ dow.f+ month.f)
fitNB2AR1 = glm.nb(days~ dow.f+ month.f + tminus1)
fitNB2AR2 = glm.nb(days~ dow.f+ month.f + tminus1+ tminus2)
fitNB2AR3 = glm.nb(days~ dow.f+ month.f + tminus1+ tminus2 + tminus3)
fitNB2AR4 = glm.nb(days~ dow.f+ month.f +
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB2AR5 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB2AR6 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB2AR7 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)

fitNB3 = glm.nb(days~ dow.f+ cos + sin)
fitNB3AR1 = glm.nb(days~ dow.f+ cos + sin + tminus1)
fitNB3AR2 = glm.nb(days~ dow.f+ cos + sin + tminus1+ tminus2)
fitNB3AR3 = glm.nb(days~ dow.f+ cos + sin + tminus1+ tminus2 + tminus3)
fitNB3AR4 = glm.nb(days~ dow.f  + cos + sin + 
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB3AR5 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB3AR6 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB3AR7 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)
```


```{r}
#Printing AICs
AR_NB1 <- c(fitNB1=fitNB1$aic,fitNB1AR1=fitNB1AR1$aic,fitNB1AR2=fitNB1AR2$aic,fitNB1AR3=fitNB1AR3$aic,
                          fitNB1AR4=fitNB1AR4$aic,fitNB1AR5=fitNB1AR5$aic,fitNB1AR6=fitNB1AR6$aic,fitNB1AR7=fitNB1AR7$aic)
AR_NB2 <- c(fitNB2=fitNB2$aic,fitNB2AR1=fitNB2AR1$aic,fitNB2AR2=fitNB2AR2$aic,fitNB2AR3=fitNB2AR3$aic,
                          fitNB2AR4=fitNB2AR4$aic,fitNB2AR5=fitNB2AR5$aic,fitNB2AR6=fitNB2AR6$aic,fitNB2AR7=fitNB2AR7$aic)
AR_NB3 <- c(fitNB3=fitNB3$aic,fitNB3AR1=fitNB3AR1$aic,fitNB3AR2=fitNB3AR2$aic,fitNB3AR3=fitNB3AR3$aic,
                          fitNB3AR4=fitNB3AR4$aic,fitNB3AR5=fitNB3AR5$aic,fitNB3AR6=fitNB3AR6$aic,fitNB3AR7=fitNB3AR7$aic)
print(AR_NB1)
print(AR_NB2)
print(AR_NB3)
```

```{r fig.width=10, fig.height=5}
plot(t,days, type="l",main="Negative Binomial Regression")
lines(fitNB1$fit, col="red"   , lwd=2)
lines(fitNB2$fit, col="blue"  , lwd=2)
lines(fitNB3$fit, col="green" , lwd=2)
legend("topleft",pch=3,col=c("red","blue","green"),
                c("Day-of-Week", "Day-of-Week+Month","Day-of-Week+sin/cos"))

```


## Chicken
```{r}
#create time series
s=2
days    <-  matrix.days[,s]
days.ts <-  ts(days, start = c(x@dates$year[1], x@dates$yday[1]),
               frequency = frequency)
t = 1:length(days)

week    <-  matrix.week[,s]
week.ts <-  ts(week, start = c(matrix.week.full[1,2],as.numeric(substr(as.character(matrix.week.full[1,1]),7,8))),
               frequency = 52)
t.week <- 1:length(week)
```

```{r fig.width=10, fig.height=5}
#Plot series
plot(days.ts , xlab="Days", main="Daily")
plot(week.ts , xlab="Weeks",main="Weeks")
```

### Summary statistics
```{r}
#Percentiles
quantile(days,probs=c(0,0.25,0.5,0.75,1),names=FALSE)
round(mean(days),4)

#Number of days at minimum value
(countInMin <- length(which(days == min(days))))
(percentInMin <- round(((countInMin)/(length(days)))*100,2))
```

```{r fig.width=10, fig.height=5}
#ACF and PACF
acf(days,main="ACF for daily data")
pacf(days,main="PACF for daily data")
```

### Crude (visual) assessment of temporal effects
```{r fig.width=10, fig.height=5}
boxplot(days ~ x@dates$dow, main="Day of the Week")
boxplot(days ~ x@dates$month, main = "Month")
boxplot(days ~ x@dates$year, main = "Year")
```

### POISSON  Regression with DOW, month or sin/cos wave
```{r}
distribution="poisson"

month.f = as.factor (x@dates$month)
dow.f <- as.factor (x@dates$dow)
cos = cos (2*pi*t/frequency)
sin = sin (2*pi*t/frequency)
tminus1<-c(days[1],days[1:(length(days)-1)])
tminus2<-c(days[1:2],days[1:(length(days)-2)])
tminus3<-c(days[1:3],days[1:(length(days)-3)])
tminus4<-c(days[1:4],days[1:(length(days)-4)])
tminus5<-c(days[1:5],days[1:(length(days)-5)])
tminus6<-c(days[1:6],days[1:(length(days)-6)])
tminus7<-c(days[1:7],days[1:(length(days)-7)])

fit1 = glm(days~ dow.f, family=distribution)
fit1AR1 = glm(days~ dow.f + tminus1, family=distribution)
fit1AR2 = glm(days~ dow.f + tminus1+ tminus2, family=distribution)
fit1AR3 = glm(days~ dow.f + tminus1+ tminus2 + tminus3, family=distribution)
fit1AR4 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit1AR5 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit1AR6 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit1AR7 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)

fit2 = glm(days~ dow.f+ month.f, family=distribution)
fit2AR1 = glm(days~ dow.f+ month.f + tminus1, family=distribution)
fit2AR2 = glm(days~ dow.f+ month.f + tminus1+ tminus2, family=distribution)
fit2AR3 = glm(days~ dow.f+ month.f + tminus1+ tminus2 + tminus3, family=distribution)
fit2AR4 = glm(days~ dow.f+ month.f +
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit2AR5 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit2AR6 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit2AR7 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)

fit3 = glm(days~ dow.f+ cos + sin, family=distribution)
fit3AR1 = glm(days~ dow.f+ cos + sin + tminus1, family=distribution)
fit3AR2 = glm(days~ dow.f+ cos + sin + tminus1+ tminus2, family=distribution)
fit3AR3 = glm(days~ dow.f+ cos + sin + tminus1+ tminus2 + tminus3, family=distribution)
fit3AR4 = glm(days~ dow.f  + cos + sin + 
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit3AR5 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit3AR6 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit3AR7 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)
```


```{r}
#Printing AICs
AR1 <- c(fit1=fit1$aic,fit1AR1=fit1AR1$aic,fit1AR2=fit1AR2$aic,fit1AR3=fit1AR3$aic,
                          fit1AR4=fit1AR4$aic,fit1AR5=fit1AR5$aic,fit1AR6=fit1AR6$aic,fit1AR7=fit1AR7$aic)
AR2 <- c(fit2=fit2$aic,fit2AR1=fit2AR1$aic,fit2AR2=fit2AR2$aic,fit2AR3=fit2AR3$aic,
                          fit2AR4=fit2AR4$aic,fit2AR5=fit2AR5$aic,fit2AR6=fit2AR6$aic,fit2AR7=fit2AR7$aic)
AR3 <- c(fit3=fit3$aic,fit3AR1=fit3AR1$aic,fit3AR2=fit3AR2$aic,fit3AR3=fit3AR3$aic,
                          fit3AR4=fit3AR4$aic,fit3AR5=fit3AR5$aic,fit3AR6=fit3AR6$aic,fit3AR7=fit3AR7$aic)


print(AR1)
print(AR2)
print(AR3)

```

```{r fig.width=10, fig.height=5}
plot(t,days, type="l",main="Poisson regression")
lines(fit1$fit, col="red"   , lwd=2)
lines(fit2$fit, col="blue"  , lwd=2)
lines(fit3$fit, col="green" , lwd=2)
legend("topleft",pch=3,col=c("red","blue","green"),
                  c("Day-of-Week", "Day-of-Week+Month","Day-of-Week+sin/cos"))

### Negative Binomial Regression with DOW, month or sin/cos wave
```{r}
require(MASS)
fitNB1 = glm.nb(days~ dow.f)
fitNB1AR1 = glm.nb(days~ dow.f + tminus1)
fitNB1AR2 = glm.nb(days~ dow.f + tminus1+ tminus2)
fitNB1AR3 = glm.nb(days~ dow.f + tminus1+ tminus2 + tminus3)
fitNB1AR4 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB1AR5 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB1AR6 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB1AR7 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)

fitNB2 = glm.nb(days~ dow.f+ month.f)
fitNB2AR1 = glm.nb(days~ dow.f+ month.f + tminus1)
fitNB2AR2 = glm.nb(days~ dow.f+ month.f + tminus1+ tminus2)
fitNB2AR3 = glm.nb(days~ dow.f+ month.f + tminus1+ tminus2 + tminus3)
fitNB2AR4 = glm.nb(days~ dow.f+ month.f +
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB2AR5 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB2AR6 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB2AR7 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)

fitNB3 = glm.nb(days~ dow.f+ cos + sin)
fitNB3AR1 = glm.nb(days~ dow.f+ cos + sin + tminus1)
fitNB3AR2 = glm.nb(days~ dow.f+ cos + sin + tminus1+ tminus2)
fitNB3AR3 = glm.nb(days~ dow.f+ cos + sin + tminus1+ tminus2 + tminus3)
fitNB3AR4 = glm.nb(days~ dow.f  + cos + sin + 
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB3AR5 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB3AR6 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB3AR7 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)
```


```{r}
#Printing AICs
AR_NB1 <- c(fitNB1=fitNB1$aic,fitNB1AR1=fitNB1AR1$aic,fitNB1AR2=fitNB1AR2$aic,fitNB1AR3=fitNB1AR3$aic,
                          fitNB1AR4=fitNB1AR4$aic,fitNB1AR5=fitNB1AR5$aic,fitNB1AR6=fitNB1AR6$aic,fitNB1AR7=fitNB1AR7$aic)
AR_NB2 <- c(fitNB2=fitNB2$aic,fitNB2AR1=fitNB2AR1$aic,fitNB2AR2=fitNB2AR2$aic,fitNB2AR3=fitNB2AR3$aic,
                          fitNB2AR4=fitNB2AR4$aic,fitNB2AR5=fitNB2AR5$aic,fitNB2AR6=fitNB2AR6$aic,fitNB2AR7=fitNB2AR7$aic)
AR_NB3 <- c(fitNB3=fitNB3$aic,fitNB3AR1=fitNB3AR1$aic,fitNB3AR2=fitNB3AR2$aic,fitNB3AR3=fitNB3AR3$aic,
                          fitNB3AR4=fitNB3AR4$aic,fitNB3AR5=fitNB3AR5$aic,fitNB3AR6=fitNB3AR6$aic,fitNB3AR7=fitNB3AR7$aic)
print(AR_NB1)
print(AR_NB2)
print(AR_NB3)
```

```{r fig.width=10, fig.height=5}
plot(t,days, type="l",main="Negative Binomial Regression")
lines(fitNB1$fit, col="red"   , lwd=2)
lines(fitNB2$fit, col="blue"  , lwd=2)
lines(fitNB3$fit, col="green" , lwd=2)
legend("topleft",pch=3,col=c("red","blue","green"),
                c("Day-of-Week", "Day-of-Week+Month","Day-of-Week+sin/cos"))

```


## Swine
```{r}
#create time series
s=3
days    <-  matrix.days[,s]
days.ts <-  ts(days, start = c(x@dates$year[1], x@dates$yday[1]),
               frequency = frequency)
t = 1:length(days)

week    <-  matrix.week[,s]
week.ts <-  ts(week, start = c(matrix.week.full[1,2],as.numeric(substr(as.character(matrix.week.full[1,1]),7,8))),
               frequency = 52)
t.week <- 1:length(week)
```

```{r fig.width=10, fig.height=5}
#Plot series
plot(days.ts , xlab="Days", main="Daily")
plot(week.ts , xlab="Weeks",main="Weeks")
```

### Summary statistics
```{r}
#Percentiles
quantile(days,probs=c(0,0.25,0.5,0.75,1),names=FALSE)
round(mean(days),4)

#Number of days at minimum value
(countInMin <- length(which(days == min(days))))
(percentInMin <- round(((countInMin)/(length(days)))*100,2))
```

```{r fig.width=10, fig.height=5}
#ACF and PACF
acf(days,main="ACF for daily data")
pacf(days,main="PACF for daily data")
```

### Crude (visual) assessment of temporal effects
```{r fig.width=10, fig.height=5}
boxplot(days ~ x@dates$dow, main="Day of the Week")
boxplot(days ~ x@dates$month, main = "Month")
boxplot(days ~ x@dates$year, main = "Year")
```

### POISSON  Regression with DOW, month or sin/cos wave
```{r}
distribution="poisson"

month.f = as.factor (x@dates$month)
dow.f <- as.factor (x@dates$dow)
cos = cos (2*pi*t/frequency)
sin = sin (2*pi*t/frequency)
tminus1<-c(days[1],days[1:(length(days)-1)])
tminus2<-c(days[1:2],days[1:(length(days)-2)])
tminus3<-c(days[1:3],days[1:(length(days)-3)])
tminus4<-c(days[1:4],days[1:(length(days)-4)])
tminus5<-c(days[1:5],days[1:(length(days)-5)])
tminus6<-c(days[1:6],days[1:(length(days)-6)])
tminus7<-c(days[1:7],days[1:(length(days)-7)])

fit1 = glm(days~ dow.f, family=distribution)
fit1AR1 = glm(days~ dow.f + tminus1, family=distribution)
fit1AR2 = glm(days~ dow.f + tminus1+ tminus2, family=distribution)
fit1AR3 = glm(days~ dow.f + tminus1+ tminus2 + tminus3, family=distribution)
fit1AR4 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit1AR5 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit1AR6 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit1AR7 = glm(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)

fit2 = glm(days~ dow.f+ month.f, family=distribution)
fit2AR1 = glm(days~ dow.f+ month.f + tminus1, family=distribution)
fit2AR2 = glm(days~ dow.f+ month.f + tminus1+ tminus2, family=distribution)
fit2AR3 = glm(days~ dow.f+ month.f + tminus1+ tminus2 + tminus3, family=distribution)
fit2AR4 = glm(days~ dow.f+ month.f +
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit2AR5 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit2AR6 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit2AR7 = glm(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)

fit3 = glm(days~ dow.f+ cos + sin, family=distribution)
fit3AR1 = glm(days~ dow.f+ cos + sin + tminus1, family=distribution)
fit3AR2 = glm(days~ dow.f+ cos + sin + tminus1+ tminus2, family=distribution)
fit3AR3 = glm(days~ dow.f+ cos + sin + tminus1+ tminus2 + tminus3, family=distribution)
fit3AR4 = glm(days~ dow.f  + cos + sin + 
                tminus1+ tminus2+ tminus3+ tminus4, family=distribution)
fit3AR5 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5, family=distribution)
fit3AR6 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6, family=distribution)
fit3AR7 = glm(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7, family=distribution)
```


```{r}
#Printing AICs
AR1 <- c(fit1=fit1$aic,fit1AR1=fit1AR1$aic,fit1AR2=fit1AR2$aic,fit1AR3=fit1AR3$aic,
                          fit1AR4=fit1AR4$aic,fit1AR5=fit1AR5$aic,fit1AR6=fit1AR6$aic,fit1AR7=fit1AR7$aic)
AR2 <- c(fit2=fit2$aic,fit2AR1=fit2AR1$aic,fit2AR2=fit2AR2$aic,fit2AR3=fit2AR3$aic,
                          fit2AR4=fit2AR4$aic,fit2AR5=fit2AR5$aic,fit2AR6=fit2AR6$aic,fit2AR7=fit2AR7$aic)
AR3 <- c(fit3=fit3$aic,fit3AR1=fit3AR1$aic,fit3AR2=fit3AR2$aic,fit3AR3=fit3AR3$aic,
                          fit3AR4=fit3AR4$aic,fit3AR5=fit3AR5$aic,fit3AR6=fit3AR6$aic,fit3AR7=fit3AR7$aic)


print(AR1)
print(AR2)
print(AR3)

```

```{r fig.width=10, fig.height=5}
plot(t,days, type="l",main="Poisson regression")
lines(fit1$fit, col="red"   , lwd=2)
lines(fit2$fit, col="blue"  , lwd=2)
lines(fit3$fit, col="green" , lwd=2)
legend("topleft",pch=3,col=c("red","blue","green"),
                  c("Day-of-Week", "Day-of-Week+Month","Day-of-Week+sin/cos"))

### Negative Binomial Regression with DOW, month or sin/cos wave
```{r}
require(MASS)
fitNB1 = glm.nb(days~ dow.f)
fitNB1AR1 = glm.nb(days~ dow.f + tminus1)
fitNB1AR2 = glm.nb(days~ dow.f + tminus1+ tminus2)
fitNB1AR3 = glm.nb(days~ dow.f + tminus1+ tminus2 + tminus3)
fitNB1AR4 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB1AR5 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB1AR6 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB1AR7 = glm.nb(days~ dow.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)

fitNB2 = glm.nb(days~ dow.f+ month.f)
fitNB2AR1 = glm.nb(days~ dow.f+ month.f + tminus1)
fitNB2AR2 = glm.nb(days~ dow.f+ month.f + tminus1+ tminus2)
fitNB2AR3 = glm.nb(days~ dow.f+ month.f + tminus1+ tminus2 + tminus3)
fitNB2AR4 = glm.nb(days~ dow.f+ month.f +
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB2AR5 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB2AR6 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB2AR7 = glm.nb(days~ dow.f+ month.f  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)

fitNB3 = glm.nb(days~ dow.f+ cos + sin)
fitNB3AR1 = glm.nb(days~ dow.f+ cos + sin + tminus1)
fitNB3AR2 = glm.nb(days~ dow.f+ cos + sin + tminus1+ tminus2)
fitNB3AR3 = glm.nb(days~ dow.f+ cos + sin + tminus1+ tminus2 + tminus3)
fitNB3AR4 = glm.nb(days~ dow.f  + cos + sin + 
                tminus1+ tminus2+ tminus3+ tminus4)
fitNB3AR5 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5)
fitNB3AR6 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6)
fitNB3AR7 = glm.nb(days~ dow.f+ cos + sin  +
                tminus1+ tminus2+ tminus3+ tminus4+ tminus5 +tminus6 +tminus7)
```


```{r}
#Printing AICs
AR_NB1 <- c(fitNB1=fitNB1$aic,fitNB1AR1=fitNB1AR1$aic,fitNB1AR2=fitNB1AR2$aic,fitNB1AR3=fitNB1AR3$aic,
                          fitNB1AR4=fitNB1AR4$aic,fitNB1AR5=fitNB1AR5$aic,fitNB1AR6=fitNB1AR6$aic,fitNB1AR7=fitNB1AR7$aic)
AR_NB2 <- c(fitNB2=fitNB2$aic,fitNB2AR1=fitNB2AR1$aic,fitNB2AR2=fitNB2AR2$aic,fitNB2AR3=fitNB2AR3$aic,
                          fitNB2AR4=fitNB2AR4$aic,fitNB2AR5=fitNB2AR5$aic,fitNB2AR6=fitNB2AR6$aic,fitNB2AR7=fitNB2AR7$aic)
AR_NB3 <- c(fitNB3=fitNB3$aic,fitNB3AR1=fitNB3AR1$aic,fitNB3AR2=fitNB3AR2$aic,fitNB3AR3=fitNB3AR3$aic,
                          fitNB3AR4=fitNB3AR4$aic,fitNB3AR5=fitNB3AR5$aic,fitNB3AR6=fitNB3AR6$aic,fitNB3AR7=fitNB3AR7$aic)
print(AR_NB1)
print(AR_NB2)
print(AR_NB3)
```

```{r fig.width=10, fig.height=5}
plot(t,days, type="l",main="Negative Binomial Regression")
lines(fitNB1$fit, col="red"   , lwd=2)
lines(fitNB2$fit, col="blue"  , lwd=2)
lines(fitNB3$fit, col="green" , lwd=2)
legend("topleft",pch=3,col=c("red","blue","green"),
                c("Day-of-Week", "Day-of-Week+Month","Day-of-Week+sin/cos"))

```


